{ \bgroup
\singlespacing

The following table defines the variables used in this paper.
Variable names and calculations provided in brackets correspond to source database. For the regressions presented in the tables, the continuous variables are winsorized at the 1st and 99th percentiles.

\begin{center}
	\centering
	\def\arraystretch{1.25}
    \footnotesize
	\begin{longtable*}{l  >{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}p{.7 \textwidth}}
        \toprule
		\textbf{Variable} 	& \textbf{Description} \\ \midrule 
		\endfirsthead
		\multicolumn{2}{c}{...continued from previous page.} \\
		\toprule
		\textbf{Variable} 	& \textbf{Description} \\ \midrule 
		\endhead
		\midrule
		\multicolumn{2}{c}{Continued on next page...} \\ 
		\endfoot
		\bottomrule
		\endlastfoot
		Assets				& Total assets $ \{ AT \} $  \\ %\hline
		Market Equity		& Market value of equity at fiscal year end. $ \{ CSHPRI * PRCC\_F \} $  \\ %\hline
		Net Income/AT 		& Net income to lagged assets. $ \{  NI_{t}/AT_{t-1}  \} $  \\ %\hline
		Operating Inc./AT 	& Operating income (after depreciation) to lagged assets. $ \{  OIADP_{t}/AT_{t-1}  \} $  \\ %\hline
		Sales Growth  		& Ratio of change in sales to lagged assets. $ \{  (SALE_t - SALE_{t-1})/AT_{t-1}  \} $  \\ %\hline
        Sales / AT  		& Sales to lagged assets. $ \{  SALE_t/AT_{t-1}  \} $  \\ %\hline
        Book Equity			& Book value of equity. $ \{ (TEQ_{t}|AT_{t} - LT_{t}) + TXDITC_{t} - PSTK_{t} \} $  \\ %\hline
		Book-to-Market  	& Book to market. $ \{ \text{Book Equity}_{t}/\text{Market Equity}_{t}  \} $  \\ %\hline
		Leverage  			& Leverage $ \{ (DLTT_{t} + DLC_{t})/AT_{t} \} $  \\ %\hline
		Tangibility  		& Tangibility $ \{ PPENT_{t}/AT_{t} \} $  \\ %\hline
		Turnover  			& Ratio of average daily volume (CRSP) to outstanding shares at fiscal year end (Compustat). \\ %\hline
		Beta  				& Market loading from CAPM model of daily returns on value weighted index, for all available days in the fiscal year. $ \{ RET = \alpha + \beta \cdot VWRETD + \epsilon \} $  \\ %\hline
        Excess Returns  	& Cumulative excess daily returns during fiscal year. $ \{ (\prod RET - VWRETD + 1) - 1  \} $  \\ %\hline
        Excess Ret. Std.	& Standard deviation of daily excess returns. $ \{ Std.\ Dev(RET- VWRETD)  \} $  \\ %\hline
        Min. Excess Ret.	& Minimum daily excess return during fiscal year. $ \{ Min(RET- VWRETD)  \} $  \\ %\hline
        Excess Ret. Skew	& Skewness of daily excess returns. $ \{ Skew(RET- VWRETD) \} $ \\ %\hline
        CAR$_{+3\ day}$  	& Cumulative abnormal return spanning three business days starting on the filing date of the annual report, using a Fama-French Carhart factor model. Data from Kenneth French's website. $ \{ RET=MKTRF+SMB+HML+UMD+MOM+\epsilon \}$ \\ %\hline
        CAR$_{+3\ months}$ 	& Cumulative abnormal return spanning 60 business days starting on the filing date of the annual report, using a Fama-French Carhart factor model. Data from Kenneth French's website. $ \{ RET=MKTRF+SMB+HML+UMD+MOM+\epsilon \}$ \\ %\hline
		Bid-Ask Spread$_{+1\ year}$ & Average daily bid ask spread at closing for 240 business days starting on the filing date of the annual report, as percentage of average bid and ask. $\{ 200*(ASK - BID)/(ASK + BID) \}$ \\ %\hline
		
		Negative NI 		& Indicator variable equal to 1 if next year's net income is negative. $ \{ NI_{t+1} < 0 \} $\\ %\hline
		Negative Op. Inc. 	& Indicator variable equal to 1 if next year's operating income is negative $ \{ OIADP_{t+1} < 0 \} $ \\ %\hline
		Sales Decline 		& Indicator variable equal to 1 if next year's sales are lower than the current year's sales by 10\%  or 10 million dollars, whichever is larger. $ \{ SALE_{t+1} - SALE_{t} < -10\%*max(100, SALE_{t}) \} $\\ %\hline
		Security Litigation	& Indicator variable equal to 1 if a securities litigation is filed in the subsequent year. \\ %\hline
		Lawsuit Intensity	& Natural log of number of litigation events found in CapitalIQ Key Developments database in a given fiscal year.\\ %\hline
		RF Comment 			& Indicator variable equal to 1 if an SEC comment letter is received in a given fiscal year that references risk factors. \\ %\hline
		Comment (Any) 		& Indicator variable equal to 1 if any SEC comment letter is received in a given fiscal year, including those with a reference to risk factors. \\ %\hline
		FPS Industry		& Indicator variable equal to 1 if the firm has an SIC code in one of the high litigation risk industries defined in \cite{francis_1994}. \\ %\hline
        
		\# Risk Factors 	& Total number of risk factors disclosed under Item 1A of an annual report. \\ %\hline
		\# New RF 			& Number of new risk factors which were not present in the previous year's annual report. \\ %\hline
   		\# Dropped RF 		& Number of risk factors which were in the previous year's annual report, but are no longer included in the present year.\\ %\hline
		\# Kept RF 			& Number of risk factors which were in the previous year's annual report and persist in the current annual report.\\ %\hline
		\# of Words 		& Total number of words in Item 1A of an annual report (excluding stop words). \\ %\hline
		\# of Sentences 	& Total number of sentences in Item 1A of an annual report.\\ %\hline
		\# of Specific Words& Total number of words identified by the Stanford Named Entity Recognition algorithm as being in categories: Location, Person, Organization \\ %\hline
		\# of Numerics 		& Total number of numbers in Item 1A of an annual report. \\ %\hline
		\# of Words/RF 		& Ratio of the total number of words to the total number of risk factors in Item 1A of an annual report (excluding stop words).\\ %\hline
		Specificity 		& Ratio of the total number of specific words to the total number of risk factors in Item 1A of an annual report (excluding stop words).\\ %\hline
		Numeric Intensity 	& Ratio of the total number of numbers to the total number of risk factors in Item 1A of an annual report (excluding stop words).\\ %\hline
		FOG Index 			& Gunning Fog score for the text in Item 1A of an annual report (excluding stop words). Calculated as $\left\{ 0.4 \left(\frac{\# \ of\ words}{\#\ of\ sentences} + 100\frac{\#\ of\ complex\ words}{\#\ of\ words}\right) \right\}$ \\ %\hline
		
	\end{longtable*}
\end{center}
\egroup
}